A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-12-28 04_Severity_MetaAnalysis.Rmd
Clean linebreaks, <br>, reformat code, etc.

This model will be similar to the grain yield meta-analysis and use the main variables:

   - *Powdery mildew severity*, the response variable (1-9 scale)

   - *Trial*, which resolves combinations of categorical random variables: 
      i) year  
      ii) location  
      iii) row spacing  
      iv) cultivar

   - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id*, random variable indicating each treatment is independent

@@

<br>  
<br>

### Define Trial
```{r define_trial}
PM_dat_D <-
   PM_dat_D %>%
   mutate(trial = paste(trial_ref,
                        year,
                        location,
                        host_genotype,
                        row_spacing,
                        sep = "_")) 
```

<!--- I would remove from this line, 77 to line 96 as we shouldn't be promoting the idea of analysing an ordinal scale directly, just go straight to the severity conversion step and describe it and why it's done (i.e., you can't analyse an ordinal scale like this, though I found a cool presentation on how to analyse an ordinal scale using metanalysis for future reference, https://methods.cochrane.org/sites/methods.cochrane.org.statistics/files/public/uploads/SMG_training_course_cardiff/2010_SMG_training_cardiff_day1_session2_lewis.pdf) -->

### Inspect PM severity for normality
Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distribution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$. We need to inspect severity for a normality.
```{r sev_hist}
hist(PM_dat_D$PM_final_severity)
summary(PM_dat_D$PM_final_severity)
```
We can see here that powdery mildew severity observations are skewed towards the top of the scale, eight and nine in this case.

We can improve the normality by transforming the effect size, disease severity, by squaring.
```{r}
PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
# Note: Here I added 1 to the variance before it was squared. This is because squaring numbers below one makes the number smaller or remain zero. This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._

hist(PM_dat_D$yi_square)
summary(PM_dat_D$yi_square)
```

Another transformation which might be more suitable for a discrete response is either a `log()` or `logit()` transformation. 
However, first we should convert the scale from 1 - 9 to between 0 and 1.

@@

Let us also transform the severity onto a percentage scale so we can compare the results of meta-analyses with no transformation, squared severity, and percent severity.

@@

```{r}
# Percent severity conversion
# define ordinal conversion from scale to proportion
s1 <- 0
s2 <- 0.33*0.5
s3 <- 0.5*0.87
s4 <- 0.66*0.75
s5 <- 0.66*0.87
s6 <- 0.66*1
s7 <- 0.75*1
s8 <- 1*0.87
s9 <- 1*1
x <- c(s1, s2, s3, s4, s5, s6, s7, s8, s9)
y <- c(1:9)
a = data.frame(x,y)
plot(a)
```

@@

```{r}
# fit a curve using a gam with spline value 0.01
g1 <- gam(x ~ s(y, spar = 0.1), family = gaussian)

# View plot of gam
plot(x = predict(g1,
                 data.frame(y = seq(1, 9, by = 0.1))), y = seq(1, 9, by = 0.1))
points(x, y, col = "red", pch = 16)

# predict values for dataset
new_sev <- predict(object =  g1, 
                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
                   )
# Check fit
plot(x = new_sev, y = PM_dat_D[,"PM_final_severity"])
points(x,y,col = "red", pch = 16)
```

@@

# Conversion of variance
# Here I add the variance and mean severity and predict the conversion value
# then subtract the mean severity to obtain the difference as the sample variance
PM_dat_D$vi_percent  <- predict(object =  g1,
                   newdata = data.frame(y = PM_dat_D[,"vi"] + PM_dat_D[,"PM_final_severity"])
                   ) - PM_dat_D$yi_percent

# create log transformed values
PM_dat_D$yi_log <- log(PM_dat_D$yi_percent)
PM_dat_D$vi_log <- (PM_dat_D$vi_percent) / (PM_dat_D$replicates * PM_dat_D$yi_percent^2)

# Correct Inf to 0
PM_dat_D[is.na(PM_dat_D$yi_log),"yi_log"] <- 0
PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001

@@

# Correct -Inf to zeros
PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0

@@

## Disease severity spray schedule meta-analysis  
First let's look at the results of the meta-analysis without transformation
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   #control = list(optimizer = "optim"),
   data = PM_dat_D
)
summary(PMsev_mv)
plot(rstandard(PMsev_mv)$z, ylim=c(-3,3), pch=19)
```

@@

```{r Metafor-Sev-analysisSQ, cache=TRUE}
PMsev_mvSQ <- rma.mv(
   yi = yi_square,
   V = vi_square,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvSQ)
plot(rstandard(PMsev_mvSQ)$z, ylim=c(-3,3), pch=19)
```
This meta-analysis is more in-line with estimates from the yield meta-analysis. `Early` sprays are not effective at reducing powdery mildew severity and two or more sprays had higher efficacy than single sprays. Recommended sprays were the most effective spray timing at reducing disease severity.

@@

Let's assess the log transformed percent severity
```{r Metafor-Sev-analysis_log, cache=TRUE}
# remove controls for response ratio meta-analysis
PMsev_mv_log <- rma.mv(
   yi = yi_log,
   V = yi_log,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mv_log)
plot(rstandard(PMsev_mv_log)$z, ylim=c(-3.2,3), pch=19)
```
The plot of the residuals show the model is not normally distributed.
In addition the estimates don't reflect what can be [observed in the raw data][Disease severity range for each spray schedule].
Log transformed percent severity is therefore no a suitable transformation

Finally let's assess the logit transformed percent severity
```{r Metafor-Sev-analysis_logitP, cache=TRUE}
# remove controls for response ratio meta-analysis
PMsev_mvPer <- rma.mv(
   yi = yi_logit,
   V = yi_logit,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

@@

# plot the model residuals
plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)

```{r Sensitivity_logitP, cache=TRUE}
s_analysis <- 
   lapply(unique(PM_dat_D$trial_ref), function(Trial) {

      dat <- filter(PM_dat_D, trial_ref != Trial)
      # remove controls for response ratio meta-analysis
      rma.mv(
         yi = yi_logit,
         V = yi_logit,
         mods = ~ spray_management,
         method = "ML",
         random = list(~ spray_management | trial, ~ 1 | id),
         struct = "UN",
         control = list(optimizer = "optim"),
         data = dat
      )

@@

length(s_analysis)
est <- lapply(s_analysis, function(e1){
   data.frame(treat = rownames(e1$b),
              estimates = e1$b,
              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
   })

@@

sensitiviy_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line(size = 1)

sensitiviy_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line(size = 1)+
   scale_y_log10()

unique(PM_dat_D$trial_ref)[7]
sensitiviy_df %>%
   group_by(treat) %>%
   summarise(minEst = min(estimates),
             medEst = median(estimates),
             maxEst = max(estimates),
             minP = min(p),
             medP = median(p),
             maxP= max(p))
```
While estimates and P values remained the mostly same when each trial was dropped from the analysis. Estimates changed the most when Trial 1617/02 at Missen Flats in 2017 was ommited from the analysis.

Calculation of I^2
```{r}
W <- diag(1/(PM_dat_D$vi_logit+0.0001))
X <- model.matrix(PMsev_mvPer)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))

100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
```
This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.

@@

      dat <- data.frame(
         estimates = inv_logit(c(intercept, m$b[-1] + intercept)),
         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
         Zval = c(inv_logit(m$z[1]),
                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
         Pval = reportP(m$pval, P_prefix = FALSE),
         CI_lb = c(inv_logit(m$ci.lb[1]), 
                       inv_logit(m$ci.lb[-1] + intercept)),
         CI_ub = c(inv_logit(m$ci.ub[1]), 
                       inv_logit(m$ci.ub[-1] + intercept)), 
         row.names = colnames(m$G)
      )
   }
   if (input_only == TRUE) {
      if (missing(intercept))
         stop("'intercept' argument is empty")
     return( inv_logit(m + intercept) - inv_logit(intercept))
   }
   return(dat)
}

@@

intercept <-PMsev_mvPer$b[1,1]
z <- PMsev_mvPer$zval[1]

@@

contrast_Ssum[6:15,] %>%
   flextable()%>%
   autofit()
```

<br>  
<br>  
<br>

@@

<br>  
<br>  
<br>

### Meta-analysis summary table
```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   pull(Freq)

@@

# create data.frame of percent disease severity estimates
results_mv <- cbind(
   data.frame(
      Moderator = c(
         "Intercept / No Spray control",
         "Early",
         "Late",
         "Late+",
         "Recommended",
         "Recommended+"
      ),
      N = k5,
      k = k6
   ),
   backtransform(PMsev_mvPer))

# Calculate mean differences
Intcpt <- results_mv$estimates[1]
results_mv <- 
   results_mv %>%
   mutate(estimates = estimates - Intcpt,
          CI_lb = CI_lb - Intcpt,
          CI_ub = CI_lb - Intcpt)

# round the numbers
results_mv[,c(4:6,8:9)] <- round(results_mv[,c(4:6,8:9)], 4)

# results_mv <- 
#    results_mv %>%
#    mutate(
#    eff_bar = round(
#       1 - estimates, 
#       4) * 100,
#    eff_CI_high = round(
#       1 - CI_lb
#    , 4) * 100,
#    eff_CI_low = round(
#       1 - CI_ub
#    , 4) * 100
#    
# )

# remove efficacy in control
#results_mv[1,10:12] <- NA

# rename colnames to give table headings
colnames(results_mv)[c(1:9 )] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "se",
     "Z",
     "P",
     "CI_{L}",
     "CI_{U}")

disease_estimates_table <-
   results_mv[c(2,5,6,3,4), -6] %>%
   flextable() %>%
   align(j = 2:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference for each spray schedule treatment to the unsprayed control treatments. Meta-analysis estimates were back transformed using an inverse logit. Data were obtained from the grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   footnote(
      i = 1,
      j = c(2:4,6:8),
      value = as_paragraph(
         c(
            "Number of treatment means categorised to each spray schedule",
            "Number of trials with the respective spray schedule",
            "Estimated mean disease severity",
            "Indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:6)],
      part = "header",
      inline = TRUE
    )%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2))%>%
   width(j = 1, width = 1) %>%
   width(j = 2, width = 0.3) %>%
   width(j = 3, width = 0.3) %>%
   width(j = 4:8, width = 0.6)

>>>>

This model will be similar to the grain yield meta-analysis and use the main variables:
   - *Powdery mildew severity*, the response variable (1-9 scale)
   - *Trial*, which resolves combinations of categorical random variables: 
      i) year
      ii) location
      iii) row spacing
      iv) cultivar
   - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.  
   - *id*, random variable indicating each treatment is independent

@@

### Define Trial

```{r define_trial}
PM_dat_D <-
   PM_dat_D %>%
   mutate(trial = paste(trial_ref,
                        year,
                        location,
                        host_genotype,
                        row_spacing,
                        sep = "_")) 
```

@@

Because the data were taken on an ordinal scale, we need to transform this to a numeric value to perform the analysis, _i.e._

> For ordinal measurements (e.g., disease rating on a 0 to 3 scale designating the ordinal degree of symptoms), nonparametric methods based on ranks should generally be used for hypothesis testing. See Shah and Madden (2004) for recommendations on the treatment of ordinal data. As an alternative, parametric proportional-odds models may be used for ordinal data, if there are sufficiently large numbers of observations for each experimental unit. If ordinal rating scores are used for ranges of disease severity (e.g., Horsfall-Barratt [where, for instance, a “2” corresponds to a severity range from 3 to 6%, and a “3” corresponds to a range of 6 to 12%]), each score should be converted to the midpoint of the corresponding disease severity range prior to use of a parametric analytical technique.

- From <https://apsjournals.apsnet.org/page/authorinformation>

@@

```{r ord-to-perc}
# Percent severity conversion
# define ordinal conversion from scale to proportion
s1 <- 0
s2 <- 0.33 * 0.5
s3 <- 0.5 * 0.87
s4 <- 0.66 * 0.75
s5 <- 0.66 * 0.87
s6 <- 0.66 * 1
s7 <- 0.75 * 1
s8 <- 1 * 0.87
s9 <- 1
x <- c(s1, s2, s3, s4, s5, s6, s7, s8, s9)
y <- c(1:9)
a = data.frame(x, y)
plot(a)
```

@@

```{r fit-gam}
# fit a curve using a gam with spline value 0.01
g1 <- gam(x ~ s(y, spar = 0.1), family = gaussian)

# View plot of the GAM
plot(x = predict(g1,
                 data.frame(y = seq(1, 9, by = 0.1))),
     y = seq(1, 9, by = 0.1))
points(x, y, col = "red", pch = 16)

# predict values for dataset
new_sev <- predict(object =  g1,
                   newdata = data.frame(y = PM_dat_D[, "PM_final_severity"]))
# Check fit
plot(x = new_sev, y = PM_dat_D[, "PM_final_severity"])
points(x, y, col = "red", pch = 16)
```

@@

# Conversion of variance
# Here I add the variance and mean severity and predict the conversion value
# then subtract the mean severity to obtain the difference as the sample variance
PM_dat_D$vi_percent  <- predict(object =  g1,
                                newdata = data.frame(y = PM_dat_D[, "vi"] + PM_dat_D[, "PM_final_severity"])) - PM_dat_D$yi_percent

# create log transformed values
PM_dat_D$yi_log <- log(PM_dat_D$yi_percent)
PM_dat_D$vi_log <-
   (PM_dat_D$vi_percent) / (PM_dat_D$replicates * PM_dat_D$yi_percent ^ 2)

# Correct Inf to 0
PM_dat_D[is.na(PM_dat_D$yi_log), "yi_log"] <- 0
PM_dat_D[PM_dat_D$vi_log == -Inf, "vi_log"] <- 0.001

@@

# Correct -Inf to zeros
PM_dat_D[is.na(PM_dat_D$yi_logit), "yi_logit"] <- 0

@@

## Disease severity spray schedule meta-analysis

First let's look at the results of the meta-analysis without transformation

```{r Metafor-Sev-analysis, cache=FALSE}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   #control = list(optimizer = "optim"),
   data = PM_dat_D
)
summary(PMsev_mv)
plot(rstandard(PMsev_mv)$z, ylim = c(-3, 3), pch = 19)
```

@@

```{r Metafor-Sev-analysisSQ, cache=FALSE}
# create transformations
PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^ 2
PM_dat_D$vi_square <- (PM_dat_D$vi + 1) ^ 2

PMsev_mvSQ <- rma.mv(
   yi = yi_square,
   V = vi_square,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvSQ)
plot(rstandard(PMsev_mvSQ)$z,
     ylim = c(-3, 3),
     pch = 19)
```

This meta-analysis is more in-line with estimates from the yield meta-analysis.
`Early` sprays are not effective at reducing powdery mildew severity and two or more sprays had higher efficacy than single sprays.
Recommended sprays were the most effective spray timing at reducing disease severity.

@@

Let's assess the log transformed percent severity.

```{r Metafor-Sev-analysis_log, cache=FALSE}
# remove controls for response ratio meta-analysis
PMsev_mv_log <- rma.mv(
   yi = yi_log,
   V = yi_log,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mv_log)
plot(rstandard(PMsev_mv_log)$z,
     ylim = c(-3.2, 3),
     pch = 19)
```

The plot of the residuals show the model is not normally distributed.
In addition the estimates don't reflect what can be [observed in the raw data][Disease severity range for each spray schedule].
Log transformed percent severity is therefore no a suitable transformation.

Finally let's assess the logit transformed percent severity.

```{r Metafor-Sev-analysis_logitP, cache=FALSE}
# remove controls for response ratio meta-analysis
PMsev_mvPer <- rma.mv(
   yi = yi_logit,
   V = yi_logit,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

@@

# plot the model residuals
plot(rstandard(PMsev_mvPer)$z,
     ylim = c(-3, 3),
     pch = 19)
```

```{r Sensitivity_logitP, cache=FALSE}
s_analysis <-
   lapply(unique(PM_dat_D$trial_ref), function(Trial) {
      dat <- filter(PM_dat_D, trial_ref != Trial)
      # remove controls for response ratio meta-analysis
      rma.mv(
         yi = yi_logit,
         V = yi_logit,
         mods = ~ spray_management,
         method = "ML",
         random = list( ~ spray_management | trial, ~ 1 | id),
         struct = "UN",
         control = list(optimizer = "optim"),
         data = dat
      )

@@

length(s_analysis)
est <- lapply(s_analysis, function(e1) {
   data.frame(
      treat = rownames(e1$b),
      estimates = e1$b,
      p = as.numeric(reportP(
         e1$pval, P_prefix = FALSE, AsNumeric = TRUE
      ))
   )
})

@@

sensitiviy_df %>%
   ggplot(aes(Tnum, estimates, colour = treat)) +
   geom_line(size = 1)

sensitiviy_df %>%
   ggplot(aes(Tnum, p, colour = treat)) +
   geom_line(size = 1) +
   scale_y_log10()

unique(PM_dat_D$trial_ref)[7]
sensitiviy_df %>%
   group_by(treat) %>%
   summarise(
      minEst = min(estimates),
      medEst = median(estimates),
      maxEst = max(estimates),
      minP = min(p),
      medP = median(p),
      maxP = max(p)
   )
```

While estimates and P values remained the mostly same when each trial was dropped from the analysis. Estimates changed the most when Trial 1617/02 at Missen Flats in 2017 was ommited from the analysis.

Calculation of I^2.

```{r}
W <- diag(1/(PM_dat_D$vi_logit+0.0001))
X <- model.matrix(PMsev_mvPer)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))

100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
```

This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.

@@

      dat <- data.frame(
         estimates = inv_logit(c(intercept, m$b[-1] + intercept)),
         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
         Zval = c(inv_logit(m$z[1]),
                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
         Pval = reportP(m$pval, P_prefix = FALSE),
         CI_lb = c(inv_logit(m$ci.lb[1]),
                   inv_logit(m$ci.lb[-1] + intercept)),
         CI_ub = c(inv_logit(m$ci.ub[1]),
                   inv_logit(m$ci.ub[-1] + intercept)),
         row.names = colnames(m$G)
      )
   }
   if (input_only == TRUE) {
      if (missing(intercept))
         stop("'intercept' argument is empty")
      return(inv_logit(m + intercept) - inv_logit(intercept))
   }
   return(dat)
}

@@

intercept <- PMsev_mvPer$b[1, 1]
z <- PMsev_mvPer$zval[1]

@@

contrast_Ssum[6:15, ] %>%
   flextable() %>%
   autofit()
```

@@

### Meta-analysis summary table

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   pull(Freq)

@@

# create data.frame of percent disease severity estimates
results_mv <- cbind(data.frame(
   Moderator = c(
      "Intercept / No Spray control",
      "Early",
      "Late",
      "Late+",
      "Recommended",
      "Recommended+"
   ),
   N = k5,
   k = k6
),
backtransform(PMsev_mvPer))

# Calculate mean differences
Intcpt <- results_mv$estimates[1]
results_mv <-
   results_mv %>%
   mutate(
      estimates = estimates - Intcpt,
      CI_lb = CI_lb - Intcpt,
      CI_ub = CI_lb - Intcpt
   )

# round the numbers
results_mv[, c(4:6, 8:9)] <- round(results_mv[, c(4:6, 8:9)], 4)

# rename colnames to give table headings
colnames(results_mv)[c(1:9)] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "se",
     "Z",
     "P",
     "CI_{L}",
     "CI_{U}")

disease_estimates_table <-
   results_mv[c(2, 5, 6, 3, 4), -6] %>%
   flextable() %>%
   align(j = 2:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference for each spray schedule treatment to the unsprayed control treatments. Meta-analysis estimates were back transformed using an inverse logit. Data were obtained from the grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   footnote(
      i = 1,
      j = c(2:4, 6:8),
      value = as_paragraph(
         c(
            "Number of treatment means categorised to each spray schedule",
            "Number of trials with the respective spray schedule",
            "Estimated mean disease severity",
            "Indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:6)],
      part = "header",
      inline = TRUE
   ) %>%
   hline_top(part = "all",
             border = officer::fp_border(color = "black", width = 2)) %>%
   width(j = 1, width = 1) %>%
   width(j = 2, width = 0.3) %>%
   width(j = 3, width = 0.3) %>%
   width(j = 4:8, width = 0.6)
